### 2021-07-03 rad-icfp-2021/correctness.tex

\begin{definition}{concategory}
    TODO
\end{definition}

\begin{definition}{free concategory}
    TODO
\end{definition}

\begin{example}{Concat1, Concat2}
    TODO
\end{example}

TODO: semantics of UN1, UNF2 inside Concat1, Concat2

@@

>>>>

One main reason for introducing UNF is to have a better control 
of the computation flow of the term, similarly to what ANF or CPS do. 
A convenient categorical setting for this is to use string diagrams.
To better fit the standard denotational semantics of languages, 
we can instead use concategories.

Concategories are a generalisation of categories and multicategories in that 
they allow morphisms both from and to a list of objects. 
Similarly to categories and multicategories, 
most categorical abstractions used for the semantics of languages are easily adapted to them.

In particular, one can form a syntactic concategory, 
which satisfies a similar universal property as syntactic multicategories.
Two such examples are of particular interest for us, 
because they will allow us to interpret Source and Target UNF, 
but also explain the UNF and $UNF^{-1}$ transformations.

\begin{example}{Concat1}
    TODO
\end{example}

We can interpret Source UNF in $\ConcatS$ as follows.

TODO

Similarly, we introduce a second concategory for the Target part.

\begin{example}{Concat2}
    TODO
\end{example}

We can interpret Target UNF in $\ConcatT$ as follows.

TODO

@@

We interpret Source in a new multicategory, 
whose morphisms are particular morphisms of $\ConcatS$.
As Source UNF is itself interpreted in $\ConcatS$, 
this gives us a way to compare terms in Source with terms in Source UNF.
This comparison precisely give the UNF transformation.
